Toward theories of deliberated preferences

### 2020-08-16 simple.tex
Repl older pref with WARP section (failure)

\subsection{Older}
A choice prediction $C_\gamma: \powersetz{\allalts} → \powersetz{\powersetz{\allalts}}$ is a mapping from each possible bundle $\emptyset ≠ B \subseteq \allalts$ to a non-empty set $\emptyset ≠ C_\gamma(B) = \mathcal{C} \subseteq \powersetz{B}$ of non-empty sets of alternatives included in the bundle. 
Thus, a generic element $\alts \in C_\gamma(B)$ satisfies $\emptyset ≠ \alts \subseteq B$. 
The choice prediction given a bundle $B$ predicts that $i$ will, given $B$, choose some indifference set that includes one of the elements $\alts \in C_\gamma(B)$.

Define $\Phi_\allalts = \set{\phi_{B, a \ind b} \suchthat \emptyset ≠ B \subseteq \allalts, a ≠ b \in B} \cup \set{\phi_{B, ¬a} \suchthat \emptyset ≠ B \subseteq \allalts, a \in B}$.

Given $a, b \in \allalts$, define $a \peq b$ iff $[a = b] \lor [\forall \set{a, b} \subseteq B: \phi_{B, a \ind b} \in \gPhi \lor \phi_{B, ¬b} \in \gPhi]$.

In order to be as resolute as possible, define an arbitrary connected ordering $>$ on $\allalts$ (a transitive, asymmetric and connected relation, connected meaning that $\forall a ≠ b \in \allalts:  [a > b \lor b > a]$), used to break indifference. Define $a \pst b$ iff $[a \peq b \land (b \npeq a \lor a > b)]$.

Note that $\peq$ is not necessarily transitive. Given $\allalts = \set{a, b, c}$, given $i$, for all $\hist \in \allhist$, define $\set{a, b}_{\hist, i} = \set{a, b}$, $\set{a, c}_{\hist, i} = \set{a}$, $\set{b, c}_{\hist, i} = \set{b, c}$, and $\set{a, b, c}_{\hist, i} = \set{a, b, c}$. Then, $\gamma$ may be valid while supporting $a \ind b$ and $b \ind c$ and have no opinion about $a$ VS $c$: indeed, neither $¬c$ nor $a \ind c$ hold. That’s because WARP is broken: $\set{a, b, c}$ contain $\set{a, c}$ and $c$ is chosen, but in $\set{a, c}$, $c$ is not chosen.

To prove. 1) If $\peq$ is transitive and the model is valid, and $a \pst b$, then $b$ is never chosen by $i$ when $a$ is present. 2) If a WARP argument is effective, then (something like) $\ipeq$ is transitive.

Consider defining $\ipeq$ and showing that $\peq$ must be a subset of it, if valid?

Perhaps, define $a \pst b$ iff $\forall \set{a, b} \subseteq B$, $a$ chosen or $b$ not chosen and sometimes both $a$ chosen and $b$ not chosen. Then define $a \ind b$ iff $\forall c \in \allalts: [a \pst c ⇔ b \pst c]$ and $\forall \set{a, b} \subseteq B$, $a$ chosen iff $b$ chosen.

>>>>

\subsection{WARP}
Note that $\peq$ is not necessarily transitive. Given $\allalts = \set{a, b, c}$, given $i$, for all $\hist \in \allhist$, define $\set{a, b}_{\hist, i} = \set{a, b}$, $\set{a, c}_{\hist, i} = \set{a}$, $\set{b, c}_{\hist, i} = \set{b, c}$, and $\set{a, b, c}_{\hist, i} = \set{a, b, c}$. Then, $\gamma$ may be valid while supporting $a \ind b$ and $b \ind c$ and have no opinion about $a$ VS $c$: indeed, neither $¬c$ nor $a \ind c$ hold. That’s because WARP is broken: $\set{a, b, c}$ contain $\set{a, c}$ and $c$ is chosen, but in $\set{a, c}$, $c$ is not chosen.

A normative theory satisfies WARP iff $[\exists \ar_{ab} \ileadstost \phi_{\set{a, b}, a} \land \exists \ar_{bc} \ileadstost \phi_{\set{b, c}, b}] ⇒ \exists \ar_{abc} \ileadstost \phi_{\set{a, b, c}, a}$.

\begin{theorem}[WARP implies transitivity]
	If an empirical theory $\gamma$ for a normative theory satisfying WARP is valid, then an empirical theory $\delta$ is valid with $\gpeq$ being transitive.
\end{theorem}
This is not enough. Need to build intermediate arguments: given $\ar_0$ for $\phi_{\set{a, b}, a}$ and $\ar_2$ for $\phi_{\set{b, c}, b}$, need $\ar = \ar_0 + \ar_2$ for $\phi_{\set{a, b, c}, a}$ that is subject to no more attacks.
